openarchaeoCollaboration

### 2021-03-12 analysis/paper.Rmd
Refine gh_commits-cum plot aesthetics

```{r dependencies, include=FALSE}
library("tidyverse")
library("lubridate")
library("openarchaeoCollaboration")
```

@@

```{r data-github}
# Warning: slow
# TODO: map
oarch <- mutate(oarch,
                gh_langs = map(oarch$gh_repo, gh_lang),
                gh_contribs = map(oarch$gh_repo, gh_contrib),
                gh_issues = map(oarch$gh_repo, gh_issue),
                gh_comments = map(oarch$gh_repo, gh_comment),
                gh_commits = map(oarch$gh_repo, gh_commit),
)
```

@@

```{r plot-gh_commits-cum}
oarch %>%
  unnest(gh_commits) %>%
  drop_na(sha) %>%
  mutate(date = floor_date(datetime, "week")) %>%
  mutate(rough_category = recode(
    rough_category,
    "Standalone apps" = "Standalone apps",
    "Packages (R, Python, etc.)" = "Packages (R, Python, etc.)",
    .default = "Other")) %>%
  group_by(rough_category, date) %>%
  summarise(n_commits = n(), .groups = "drop_last") %>%
  mutate(cat_total = sum(n_commits)) %>%
  mutate(cum_commits = cumsum(n_commits)) %>%
  ggplot(aes(date, cum_commits,
             fill = fct_reorder(rough_category, cat_total))) +
  geom_area() +
  scale_x_datetime(limits = c(ymd("2008-01-01", tz = "UTC"), NA),
                   date_breaks = "2 years",
                   date_labels = "%Y") +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "Open source archaeology",
    subtitle = "Cumulative commits in GitHub repositories",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = NULL, y = "Commits", fill = NULL
  ) +
  theme(legend.position = "bottom")
```

>>>>

```{r dependencies, include=FALSE}
library("tidyverse")
library("lubridate")
library("openarchaeoCollaboration")
library("khroma")
```

@@

```{r data-github}
# Warning: slow
oarch <- mutate(oarch,
                gh_langs = map(oarch$gh_repo, gh_lang),
                gh_contribs = map(oarch$gh_repo, gh_contrib),
                gh_issues = map(oarch$gh_repo, gh_issue),
                gh_comments = map(oarch$gh_repo, gh_comment),
                gh_commits = map(oarch$gh_repo, gh_commit)
)
```

@@

```{r plot-gh_commits-cum}
oarch %>%
  unnest(gh_commits) %>%
  drop_na(sha) %>%
  mutate(date = floor_date(datetime, "week")) %>%
  mutate(rough_category = recode(
    rough_category,
    "Standalone apps" = "Standalone apps",
    "Packages (R, Python, etc.)" = "Packages (R, Python, etc.)",
    .default = "Other")) %>%
  group_by(rough_category, date) %>%
  summarise(n_commits = n(), .groups = "drop_last") %>%
  mutate(cat_total = sum(n_commits)) %>%
  mutate(cum_commits = cumsum(n_commits)) %>%
  ggplot(aes(date, cum_commits,
             fill = fct_reorder(rough_category, cat_total),
             colour = fct_reorder(rough_category, cat_total))) +
  geom_area() +
  scale_x_datetime(limits = c(ymd("2008-01-01", tz = "UTC"), NA),
                   date_breaks = "1 years",
                   date_labels = "%Y") +
  scale_colour_contrast(guide = NULL) +
  scale_fill_contrast(guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "Open Archaeology",
    subtitle = "Cumulative commits in GitHub repositories",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = NULL, y = NULL, fill = NULL
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "IBM Plex Sans"),
    legend.position = "bottom", 
    legend.justification = "right",
    legend.margin = margin(),
    legend.box.margin = margin()
  )
```
